Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-06-21 analysis/paper/paper.Rmd
added density and kernel density plot

# transform data to PPP format and sp SpatialPoints
library(spatstat)

@@

# create ppp
ornaments_point <- ppp(lon, lat, xrange, yrange)

>>>>

# transform data to PPP format and sp SpatialPoints
library(spatstat)
library(maptools)
library(raster)

@@

# create ppp and sp(spacial points) format
ornaments_point_ppp <- ppp(lon, lat, xrange, yrange)
ornaments_point_sp <- as(ornaments_point_ppp, "SpatialPoints")
r_ornaments <- raster(sample_units)

# plot density
den_ornaments <- rasterize(coordinates(ornaments_point_sp), r_ornaments, fun = 'count', background = 0)
plot(den_ornaments)

# kernel density estimation
ds <- density(ornaments_point_ppp)
plot(ds, main = "Ornament density")

kernel_or <- density(ornaments_point_ppp)
kernel_or %>%  # Using the default bandwidth
  plot(main= "Ornament density", las=1)
contour(kernel_or, add=TRUE)
```
